\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{orcidlink}
\pagestyle{empty}
\setlength{\parindent}{0pt}

\begin{document}

{\large\bfseries Title Page}\\[1.2em]

{\Large\bfseries Pan-Andean explainable machine learning identifies priority
glacial lakes for outburst flood early warning\par}

\vspace{2em}

{\bfseries Authors}\\[0.6em]
Richar Andre Vilca-Solorzano\textsuperscript{1,*}\\
\hspace*{1em}ORCID: \href{https://orcid.org/0009-0003-2385-5263}{0009-0003-2385-5263}\\[0.4em]
Dina Maribel Yana-Yucra\textsuperscript{1}\\
\hspace*{1em}ORCID: \href{https://orcid.org/0009-0003-6218-2735}{0009-0003-6218-2735}\\[0.4em]
Milton Vladimir Mamani-Calisaya\textsuperscript{1}\\
\hspace*{1em}ORCID: \href{https://orcid.org/0000-0002-0676-0989}{0000-0002-0676-0989}\\[0.4em]
Fred Torres-Cruz\textsuperscript{1}\\
\hspace*{1em}ORCID: \href{https://orcid.org/0000-0003-0834-6834}{0000-0003-0834-6834}\\

\vspace{1.5em}

{\bfseries Affiliation}\\[0.6em]
\textsuperscript{1}\,Faculty of Statistical and Computer Engineering,
Universidad Nacional del Altiplano (UNAP), Puno, Peru.

\vspace{1.5em}

{\bfseries Corresponding author}\\[0.6em]
Richar Andre Vilca-Solorzano\\
Faculty of Statistical and Computer Engineering,\\
Universidad Nacional del Altiplano (UNAP), Puno, Peru\\
E-mail: \href{mailto:75521963@est.unap.edu.pe}{75521963@est.unap.edu.pe}

\vspace{2em}

{\bfseries Statements and Declarations}\\[0.6em]
\textit{Funding.} The authors declare that no funds, grants, or other
support were received during the preparation of this manuscript.\\[0.4em]
\textit{Competing Interests.} The authors have no relevant financial or
non-financial interests to disclose.\\[0.4em]
\textit{Ethics approval.} Not applicable.\\[0.4em]
\textit{Consent to participate / publish.} Not applicable.\\[0.4em]
\textit{Author Contributions.} Richar Andre Vilca-Solorzano conceptualized
the study, developed the methodology, performed the formal analysis and
visualization, and wrote the original draft. Dina Maribel Yana-Yucra
contributed to data curation, validation, and writing -- review \& editing.
Milton Vladimir Mamani-Calisaya and Fred Torres-Cruz contributed to
supervision, resources, and critical review of the manuscript. All authors
read and approved the final manuscript.\\[0.4em]
\textit{Data Availability.} Inventory, models, SHAP values, and the
reproducible pipeline are openly available at
\url{https://github.com/Andre031222/pan-andean-glof-susceptibility}
(Zenodo DOI on acceptance).

\end{document}
